Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2021-02-10 _03_smoothing_tracks.Rmd
add speed histogram code

```{r read_sim_data_2}
# read in the data and set the window size variable
data <- fread("data/data_sim.csv")[5000:10000, ]
data[, window_size := NA]

@@

```{r}
# bind list after offset
data_plot <- mapply(function(df, offset) {
  df[, x := x + offset]
}, list_of_smooths, seq(0.4, 1.25, length.out = 4),
SIMPLIFY = F
)

data_plot <- rbindlist(data_plot)
```

@@

```{r echo=FALSE}
# prepare data to plot
# make list of data to plot
figure_median_smooth <-
  ggplot() +
  geom_point(
    data = data_errors,
    aes(x, y),
    col = pal[3],
    size = 0.2
  ) +
  geom_path(
    data = data,
    aes(x, y),
    col = "grey20",
    lwd = 0.5
  ) +
  geom_path(
    data = data_plot,
    aes(x, y,
      col = window_size,
      group = window_size
    ),
    show.legend = F,
    lwd = 0.5
  ) +
  coord_equal(
    expand = F,
    ylim = c(0.6, 0.85),
    xlim = c(NA, 2.3),
    ratio = 1.75
  ) +
  annotate(
    geom = "text",
    x = c(0.75, seq(1.1, 2, length.out = 4)),
    y = 0.82,
    label = sprintf("(%s)", letters[seq(5)]),
    fontface = "bold"
  ) +
  scale_colour_distiller(
    palette = "Purples", direction = 1,
    values = c(-0.5, 1)
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  )

>>>>

```{r read_sim_data_2}
# read in the data and set the window size variable
data <- fread("data/data_sim.csv")[5000:10000, ]
data[, window_size := NA]
data$speed_in = atl_get_speed(data)

@@

```{r}
# bind list after offset
data_plot <- mapply(function(df, offset) {
  df = copy(df)
  df[, x := x + offset]
  df$speed_in = atl_get_speed(df)
  return(df)
}, list_of_smooths, seq(0.4, 1.25, length.out = 4),
SIMPLIFY = F
)

data_plot <- rbindlist(data_plot)

# add offset to data errors
data_errors = lapply(c(0, seq(0.4, 1.25, length.out = 4)),
                     function(offset) {
  df = copy(data_errors)
  df[,x := x + offset]
  df[, offset := offset]
})

# bind list
data_errors = rbindlist(data_errors)
```

```{r}
pal2 = RColorBrewer::brewer.pal(4, "RdPu")[c(2, 4)]

fig_hist_smooth =
  ggplot()+
  geom_histogram(
    data = data_errors[offset == 0,],
    aes(x = in_speed,
        fill = "errors"),
    bins = 80,
    alpha = 1
  )+
  geom_histogram(
    data = data_plot[window_size %in% c(5, 21)],
    aes(x = speed_in,
        fill = as.factor(window_size),
        group = window_size),
    bins= 80
  )+
  geom_histogram(
    data = data,
    aes(x = speed_in,
        fill = "real"),
    # col = pal[1],
    alpha = 0.8,
    bins = 80
  )+
  scale_x_log10()+
  scale_fill_manual(
    values = c(
      "real" = alpha("grey20", .8),
      "errors" = "grey",
      "5" = pal2[1],
      "21" = pal2[2]
    ),
    labels = c(
      "real" = "real track",
      "errors" = "track w/\nerrors",
      "5" = "K = 5",
      "21" = "K = 21"
    )
  )+
  coord_cartesian(xlim = c(1e-5, .05))+
  theme_test(base_family = "sans")+
  theme(
    legend.position = c(0.2, 0.65),
    axis.text = element_blank(),
    # axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(
      face = "bold"
    ),
    plot.background = element_blank()
  )+
  labs(x= "Speed [log10 scale]",
       fill = "Smoothing",
       title = "(f)")
```

@@

```{r echo=FALSE}
# prepare data to plot
# make list of data to plot
figure_median_smooth <-
  ggplot() +
  geom_path(
    data = data_errors,
    aes(x, y,
        group = offset),
    col = "grey60",
    size = 0.1
  ) +
  geom_point(
    data = data_errors[offset == 0,],
    aes(x, y),
    col = pal[3],
    size = 0.2
  ) +
  geom_path(
    data = data,
    aes(x, y),
    col = "grey20",
    lwd = 0.5
  ) +
  geom_path(
    data = data_plot,
    aes(x, y,
      group = window_size,
      col = window_size
    ),
    show.legend = F,
    lwd = 0.3
  ) +
  coord_equal(
    expand = F,
    ylim = c(0.6, 0.85),
    xlim = c(NA, 2.3),
    ratio = 1.75
  ) +
  annotate(
    geom = "text",
    x = c(0.75, seq(1.1, 2, length.out = 4)),
    y = 0.82,
    label = sprintf("(%s)", letters[seq(5)]),
    fontface = "bold"
  ) +
  scale_colour_distiller(
    palette = "RdPu", direction = 1,
    values = c(-1, 1)
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  )

# # wrap figures
# figure_median_smooth =
#   wrap_plots(figure_median_smooth,
#              fig_hist_smooth,
#              design = "AAAA\nBB##")
